%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{tabularray}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}

\usepackage[most]{tcolorbox}
\tcbset{
    frame code={}
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-2mm,
    boxsep=4pt,
    arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}


\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]


%------------ CUSTOM COMMANDS -------------
\newcommand{\bluetext}[1]{\textcolor{blue}{#1}}

\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} & \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeDiplome}[2]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{ #1} & \footnotesize{#2}
    \end{tabular*}
    \vspace{-7mm}
}

\newcommand{\resumeProject}[2]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.99\textwidth}[t]{
    @{}p{\dimexpr0.40\textwidth-\tabcolsep}@{\hspace{\tabcolsep}} 
    @{\extracolsep{\fill}}r}
        \textbf{ #1} & \footnotesize{#2}
    \end{tabular*}
    \vspace{-7mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

\definecolor{textcol}{RGB}{0,0,0}
\definecolor{pygray}{HTML}{646464}

\newcommand{\iconref}[2]{\textcolor{#1}{\csname fa#2\endcsname}}    
\newcommand{\iconweb}[5]{                         
    \href{https://www.#5}{\vcenteredhbox{\iconref{#1}{#2}} \textcolor{#3}{#4}}
}

\newcommand{\textweb}[2]{                         
    \href{https://www.#1}{\vcenteredhbox{\textcolor{textcol}{#2}}}
}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
\newcommand{\name}{ACHRAF NAJMI}
\newcommand{\descriptionTitle}{SysAdmin \& DevOps Engineer}
\newcommand{\skillsNote}{Infrastructure, Security \& DevOps}
\newcommand{\map}{Lyon, France}
\newcommand{\phone}{+33 7 53 00 43 62}
\newcommand{\email}{najmi.achraf@gmail.com}
\newcommand{\linkedin}{linkedin.com/in/najmiachraf}
\newcommand{\linkedinLink}{https://www.linkedin.com/in/najmiachraf}
\newcommand{\github}{github.com/NajmiAchraf}
\newcommand{\githubLink}{https://www.github.com/NajmiAchraf}

\usepackage[default]{raleway}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}
\usepackage{moresize}

\begin{document}

%----------HEADING-----------------

\parbox{\dimexpr\linewidth-0.0cm\relax}{
    \parbox[b][45pt][c]{0.43\textwidth}{
        \begin{tabularx}{\linewidth}{l}
           \textbf{\HUGE{\name}}\\
           \textsc{\Large \descriptionTitle} \\
           \textit{\small \textcolor{pygray}{\skillsNote}}
        \end{tabularx}
    }&
    \parbox[b][45pt][c]{0.56\textwidth}{
        \begin{tabularx}{\linewidth}{l @{\hspace{0.5em}} l}
           \href{mailto:\email}{\raisebox{0.0\height}{\footnotesize \faEnvelope}\ {\email}} & \href{\linkedinLink}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ {\linkedin}}\\
           {\raisebox{0.0\height}{\footnotesize \faMobile}\ \phone} & \href{\githubLink}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {\github}}\\
           {\raisebox{0.0\height}{\footnotesize \faMapMarker}\ \map} & \\
        \end{tabularx}
    }
}

\small

%-----------PROFESSIONAL SUMMARY-----------
\section{\textbf{Professional Summary}}
  \resumeSubHeadingListStart
    \textbf{}{IT Engineering student specializing in infrastructure, network security, and automated deployments. Strong foundation in Linux server administration, virtualization (VMware/KVM), and modern DevOps tools.}
    \newline
    \textbf{}{Experienced in deploying, supervising, and securing critical IT systems. Skilled at bridging traditional system administration rigor with scalable automation pipelines and cloud-native infrastructure.}
  \resumeSubHeadingListEnd
\vspace{-5.5mm}

%-----------TECHNICAL SKILLS-----------------
\section{\textbf{Technical Skills}}
\vspace{5pt}
\centering
\begin{tblr}{
  colspec = {|cl|cl|cl|cl|cl|},
  rowsep=0.1em,
  colsep=0.3em,
}
    \hline
    \SetCell[c=2]{c} \textbf{SysAdmin \& Network} & & \SetCell[c=2]{c} \textbf{Web \& Security} & & \SetCell[c=2]{c} \textbf{DevOps \& Virtualization} & & \SetCell[c=2]{c} \textbf{Scripting \& Code} \\
    \hline
    \faIcon{linux} & Linux / MacOS & \faIcon{server} & Apache / NGINX & \faIcon{cogs} & KVM / VMware & \faIcon{terminal} & Bash / Zsh \\
    \faIcon{network-wired} & TCP/IP \& Routing & \faShieldAlt & SSL / Firewalls & \faIcon{docker} & Docker / K8s & \faPython & Python \\
    \faIcon{desktop} & Nagios / Monitoring & \faIcon{key} & SSH / LDAP & \faIcon{infinity} & CI/CD Pipelines (ArgoCD) & \faDatabase & SQL / PostgreSQL \\
    \faIcon{microchip} & Backup Systems & \faWordpress & CMS Management & \faCodeBranch & Git / GitLab & \faCode & C / C++ \\
    \hline
\end{tblr}
\vspace{-5pt}

%-----------PROFESSIONAL EXPERIENCE-----------
\section{\textbf{Professional Experience}}
  \resumeSubHeadingListStart
  \resumeDiplome
  {\textweb{toubkal.um6p.ma}{Toubkal Supercomputer} - \textweb{cc.um6p.ma}{College Of Computing} - \textweb{um6p.ma/en/um6p-college-computing}{UM6P}}{06/24 - 03/26}
   \begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
      \textbf{Quantum Software Engineer} \textit{(Internship to Full-Time Role)} \\
    }}
    \end{itemize}
  \vspace{-5mm}
  \resumeItemListStart
    \item {Executed high-dimensional simulations on HPC environments, mastering resource allocation via SLURM.}
    \item {Developed optimized Python frameworks for data manipulation, applying rigorous scripting to solve complex tasks.}
  \resumeItemListEnd
  \vspace{-3mm}
  \resumeSubHeadingListEnd
\vspace{-5.5mm}

%-----------TECHNICAL PROJECTS & 42 CURSUS-----------
\section{\textbf{Technical Projects \& 42 Cursus}}
\resumeSubHeadingListStart
    
    \resumeProject
    {Kubernetes: Inception-of-Things}
    {\faUser Solo | \faIcon{cogs} Kubernetes, K3d}
   \begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
      \iconweb{pygray}{Github}{pygray}{github.com/NajmiAchraf/Inception-of-Things}{github.com/NajmiAchraf/Inception-of-Things}
    }}
    \end{itemize}
  \vspace{-5mm}
    \resumeItemListStart
        \item {Deployed a multi-node Kubernetes cluster utilizing K3d to virtualize infrastructure environments.}
        \item {Implemented a complete CI/CD workflow utilizing GitOps methodologies and ArgoCD for automated synchronization.}
    \resumeItemListEnd
    \vspace{-2mm}
    
    \resumeProject
    {Linux Administration: Born2beroot}
    {\faUser Solo | \faIcon{linux} Debian, Bash}
   \begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
      \iconweb{pygray}{Github}{pygray}{github.com/NajmiAchraf/Born2beroot}{github.com/NajmiAchraf/Born2beroot}
    }}
    \end{itemize}
  \vspace{-5mm}
    \resumeItemListStart
        \item {Installed and configured a virtual machine (Debian) setting up a secure server environment from scratch.}
        \item {Configured strict LVM partitions, UFW firewalls, SSH policies, and wrote automated Bash scripts for system monitoring.}
    \resumeItemListEnd
    \vspace{-2mm}
    
    \resumeProject
    {Docker Infrastructure: Inception}
    {\faUser Solo | \faIcon{docker} Docker, WordPress}
   \begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
      \iconweb{pygray}{Github}{pygray}{github.com/NajmiAchraf/Inception}{github.com/NajmiAchraf/Inception}
    }}
    \end{itemize}
  \vspace{-5mm}
    \resumeItemListStart
        \item {Engineered a complete LEMP stack infrastructure using custom Docker containers built on Alpine Linux.}
        \item {Configured secure networks, NGINX web servers with SSL/TLS, MariaDB, and deployed a WordPress CMS backend.}
    \resumeItemListEnd
    \vspace{-2mm}
    
    \resumeProject
    {HTTP Server: Webserv}
    {\faIcon{users} Team | \faCode C++, HTTP/1.1}
   \begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
      \iconweb{pygray}{Github}{pygray}{github.com/NajmiAchraf/Webserv}{github.com/NajmiAchraf/Webserv}
    }}
    \end{itemize}
  \vspace{-5mm}
    \resumeItemListStart
        \item {Implemented a fully compliant HTTP/1.1 web server from scratch without external libraries.}
        \item {Handled socket programming, port multiplexing (epoll), routing, and secure request parsing.}
    \resumeItemListEnd
    \vspace{-2mm}
    
    \resumeProject
    {Advanced Curriculum \& Common Core}
    {\faIcon{star} Specialization | \faIcon{cloud} Infrastructure \& DevOps}
   \begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
      \iconweb{pygray}{Github}{pygray}{github.com/NajmiAchraf/42cursus}{github.com/NajmiAchraf/42cursus}
    }}
    \end{itemize}
  \vspace{-5mm}
    \resumeItemListStart
        \item {\textbf{Cloud \& DevOps:} Orchestrated Kubernetes clusters, Docker containerization, and CI/CD pipelines.}
        \item {\textbf{Systems Administration:} Custom Shell (\textit{Minishell}), HTTP Server (\textit{Webserv}), and network configuration.}
        \item {\textbf{Graphics \& Math:} Built a raycasting engine (\textit{cub3d}) and fractal renderer (\textit{fract-ol}) using C and MinilibX.}
    \resumeItemListEnd
    \vspace{-2mm}
\resumeSubHeadingListEnd
\vspace{-5.5mm}

%-----------EDUCATION-----------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
  \resumeDiplome
  {\textweb{42lyon.fr}{42 Lyon Auvergne-Rhône-Alpes} - \textweb{campusnumerique.auvergnerhonealpes.fr}{Campus Région du numérique}}{2026 - Present}
   \begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
      \textbf{Candidate for RNCP Level 7 Title: Expert in IT Architecture} \textit{\footnotesize{(Transfer from 1337 Coding School)}}
    }}
    \end{itemize}
  \vspace{-5mm}
  \resumeItemListStart
    \item {Specialization in Data Science, Advanced Algorithms, Systems Architecture, and Distributed Infrastructure.}
  \resumeItemListEnd
  \vspace{-2mm}
  \resumeDiplome
  {\textweb{1337.ma/en/}{1337 Coding School} - \textweb{um6p.ma/en/ecole-1337}{University Mohammed VI Polytechnic}}{2021 - 2026}
   \begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
      \textbf{Conception \& Architecture of Information Systems}{}
      \textit{\footnotesize{42 Network}}\\
    }}
    \end{itemize}
  \vspace{-5mm}
  \resumeItemListStart
    \item {Completed the Common Core (C/C++, System Architecture, UNIX).}
  \resumeItemListEnd
  \vspace{-2mm}
  \resumeDiplome
  {\textweb{fsb.univh2c.ma/}{Faculty of Science Ben M'sik - University Hassan II}}{End: 2019}
   \begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
      \textbf{Bachelor's Degree in Physics (Material Science)}{} \\
    }}
    \end{itemize}
  \vspace{-5mm}
  \resumeItemListStart
    \item {Strong mathematical foundation: Differential equations, Statistics, and Linear Algebra.}
  \resumeItemListEnd
  \vspace{-2mm}
  \resumeSubHeadingListEnd
\vspace{-5.5mm}

%-----------Soft Skills-----------------
\section{\textbf{Soft Skills \& Languages}}
\vspace{5pt}
 \begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
      \textbf{Languages: }{French (Professional Working Proficiency), English (Professional Working Proficiency), Arabic (Native)} \\
      \textbf{Soft Skills: }{Analytical Thinking, Research Rigor, Cross-functional Communication, Collaborative Problem Solving, Adaptability.}
    }}
 \end{itemize}

\end{document}